\section{Background}
\label{section:background}

There are various solutions that can be used to build VPNs. One example is 
Host Identity Protocols (HIP)~\cite{gurtov2008host}. HIP is a layer 3.5 
solution (it is in fact located between transport and network layers) and 
was originally designed to split the dual role of IP addresses - identifier 
and locator. For example, a company called Tempered Networks uses HIP 
protocol to build secure networks (for sampling see~\cite{temperednetworks}).

Another solution is Secure Shell protocol (or SSH)~\cite{ssh}. SSH is an 
application layer protocol, which provides an encrypted channel for insecure 
networks. SSH was originally designed to provide secure remote command-line, 
login, and command execution. But in fact,  any network service can be secured 
with SSH. Moreover, SSH provides means for creating VPN tunnels between the 
spatially separated networks. Unfortunately, SSH connection can be analyzed 
and blocked (would it be as widely spread as for example  TLS protocol, 
things could be different).

Like SSH, OpenVPN~\cite{openvpn} runs on top of TCP protocol (in fact,
OpenVPN can also operate on top of UDP transport protocol).
We have evidence that in certain countries OpenVPN is successfully blocked 
by governments. Of course, it is harder to detect these protocols, because 
traffic is encapsulated inside TCP/UDP connections. Here, deep packet 
inspection solutions are required in order to effectively block such tunnels.

Another widely used layer 3 protocol for building the VPNs is IPSec 
protocol~\cite{ipsec}. In IPSec security association can be established 
using pre-shared keys or using Internet Key Exchange protocols (IKE and 
IKEv2)~\cite{ike}. Because IPsec runs directly on top of IP protocol, it 
can be easily detected without the usage of sophisticated packet inspection 
solutions.
  